Collaborative Visual Analysis on the Web with RCloud

### 2015-06-26 interviews.tex
remove comments
use same inline headlines
a few lines, hey
also improve some topic sentences

\subsection{Sharing of results}
Sharing of notebooks is the core feature of RCloud, and a popular one. All
the subjects praised this feature.

By default, all RCloud notebooks are publicly visible, and notebooks can be
found by navigating the notebook tree, or by searching. However, users most
often mentioned sharing by sending links through email. Lilo says,
``If my supervisor wants to see what I've done or QA it, I can just send her a link.''

@@

\subsection{Forking}
The ability to fork someone's notebook and continue their work was popular, but it
should probably not be the only way to change notebooks.
Almost twice as many (131) users have forked
someone else's notebook as have starred one (75). Lilo says, ``It's one of the
handiest functions, because instead of having to find it, copy, paste it, you
just hit Fork, rename it, and it's done. It's pretty amazing.''

Although we intended forking to be available to improve others' code, we
didn't anticipate forking one's own notebooks, which
proved very useful. Kenyon says, ``I fork my own notebooks because I'm going off
and doing some other analogous project, so I've got interesting content that I've
already done in a previous analysis, that I want to start from and then tweak
to match a new set of data.''

@@

\subsection{Automatic source control}
Automatic source control is helpful, but it also leads to many commits. Lilo says, ``Instead of
looking back and saying I've got a billion files here in this subdirectory and I
hope I've got them backed up, if they're on RCloud I know they are.''

@@

\subsection{Discovering others' work}
Users reported that the search function is more helpful for learning about
particular functions than techniques. Wendy says, ``The fact that we have
all the notebooks there, searchable, saves me from replicating what other people
have done.''
But other users prefer to browse just the notebooks of experts they
know. Kenyon says, ``Usually I know somebody's notebooks that I want to search
through, because \comment{I know that} the kind of thing I'm looking for is something
more obscure than I'm likely to find in some random person's.''
More selective ways to search will be needed as the number of notebooks
grows further. We mention possible approaches in Section~\ref{sec:discussion}.

\subsection{Integrated analysis}
Integrating an analysis language into a web development environment is something
tool developers really appreciate. The structure of Hugh's visualization
notebook means
\begin{quote}
the other guys who want to do analytics on the data can first pull
the data, do the analytics on it, and then feed the viewer the data.
Anyone from the stats group can insert something in between.
Once you get the data into RCloud, then you have a dataframe
to work with, and then they can produce another dataframe.
\end{quote}

Integrating R helps Allison's application: ``Having an open session where I can run R commands or
functions without having to invoke an API or send a request and then
wait for the response is extremely helpful in writing the application.''

\subsection{Blocked by the web}

Although most analysts appreciated RCloud's sharing features,
it was not a popular tool for exploratory data analysis.
All analysts with R experience prefered to do analysis in another
tool, then paste code into RCloud for sharing, because the web interface got in the
way of their work.

@@

\subsection{Cells versus the command line}
RCloud's notebook interface combines editable Markdown with a command line
interface. Many users felt that this format, so effective for presentation,
is incompatible with exploratory data analysis.

@@

\subsection{Too vertical}
The strict vertical linearity of a notebook also poses space and time problems
not encountered on the command line, where typically only the last few lines are looked.

@@

\subsection{A sea of notebooks}
RCloud is becoming a victim of its own success, as it is becoming
difficult to navigate all the notebooks. There are over 5200 notebooks in
the research instance, of which more than 500 have been starred, and more
than 350 have been forked.

@@

%% Iris: ``One UI notebook and a bunch of other notebooks that do various tasks and
%% are called with API calls. The problem is, if you clone all the notebooks, then
%% you have to go update every single notebook, because all the IDs are different
%% now. There's no sort of relative path type stuff that you can do. You can do it
%% with static assets, but you can't do it with Ajax calls''

>>>>

\paragraph*{Sharing of results} is the core feature of RCloud, and a popular one. All
the subjects praised this feature.

By default, all RCloud notebooks are publicly visible, and notebooks can be
found by navigating the notebook tree, or by searching. However, users most
often mentioned sharing by sending links through email.

@@

\paragraph*{Forking} The ability to fork someone's notebook and continue their
work proves to be a useful feature, but it is a lousy way to change simple parameters.
Almost twice as many (131) users have forked
someone else's notebook as have starred one (75). Lilo says, ``It's one of the
handiest functions, because instead of having to find it, copy, paste it, you
just hit Fork, rename it, and it's done. It's pretty amazing.''

Although we intended forking to be available to improve others' code, we
didn't anticipate users forking their own notebooks, which
proved very useful. Kenyon says, ``I fork my own notebooks because I'm going off
and doing some other analogous project, so I've got interesting content that I've
already done in a previous analysis, that I want to start from and then tweak
to match a new set of data.''

@@

\paragraph*{Automatic source control} is appreciated for its safety and ease,
but the large number of commits can be hard to manage. Lilo says, ``Instead of
looking back and saying I've got a billion files here in this subdirectory and I
hope I've got them backed up, if they're on RCloud I know they are.''

@@

\paragraph*{Discovering others' work} Users reported that the search function is
more helpful for learning about
particular functions than techniques. Wendy says, ``The fact that we have
all the notebooks there, searchable, saves me from replicating what other people
have done.''

But other users prefer to browse just the notebooks of experts they
know. Kenyon says, ``Usually I know somebody's notebooks that I want to search
through, because \comment{I know that} the kind of thing I'm looking for is something
more obscure than I'm likely to find in some random person's.''
More selective ways to search will be needed as the number of notebooks
grows further. We mention possible approaches in Section~\ref{sec:discussion}.

\paragraph*{Integrated analysis} Integrating an analysis language into a web
development environment is something tool developers really appreciate.
The structure of Hugh's visualization notebook means
\begin{quote}
the other guys who want to do analytics on the data can first pull
the data, do the analytics on it, and then feed the viewer the data.
Anyone from the stats group can insert something in between.
Once you get the data into RCloud, then you have a dataframe
to work with, and then they can produce another dataframe.
\end{quote}

Integrating R makes Allison's application development easier:
``Having an open session where I can run R commands or
functions without having to invoke an API or send a request and then
wait for the response is extremely helpful in writing the application.''

\paragraph*{Web is limiting} Although most analysts appreciated RCloud's sharing features,
it was not a popular tool for exploratory data analysis.
All analysts with R experience prefered to do analysis in another
tool, then paste code into RCloud for sharing, because the web interface got in the
way of their work.

@@

\paragraph*{Impermeable cells} RCloud's notebook interface combines editable
Markdown with a command line
interface. Many users felt that this format, so effective for presentation,
is incompatible with exploratory data analysis.

@@

\paragraph*{Too vertical} The vertical orientation of a notebook also poses problems
not encountered on the command line, where typically only the last few page of output matters.

@@

\paragraph*{A sea of notebooks} RCloud is becoming a victim of its own success, as it is becoming
difficult to navigate all the notebooks. There are over 5200 notebooks in
the research instance, of which more than 500 have been starred, and more
than 350 have been forked.

@@
